---
title: "Largest Prime Factor"
output: html_document
---

## Largest Prime Factor

### Problem Description

The prime factors of 13195 are 5, 7, 13 and 29.

What is the largest prime factor of the number 600851475143 ?

_(answer 6857)_

### Solution

Use the numbers library to get the prime factors.

```{r}
require(numbers)
largest_prime_factor <- function(num) {
  max(primeFactors(num))
}
```

### Tests

Execute a euler test for the function:
If the test fails knitter won't compile to html.

```{r}
library(testthat)
test_that("check euler question", {
  expect_equal(6857, largest_prime_factor(600851475143))
})
```

## Retrospective

First attempt at implementing a euler problem as Rmarkdown.

Testing could be better in the sense that Runit seems to need to be give a
filename or regex to parse tests from, making inline testing difficult.
Testthat seems more useful but does not have the option to give any output
for inline tests when they pass. This would be useful in a Markdown document
to demonstrate the passing tests.


